---
title: "Plotly"
author: "Maya Spaur"
date: "10/22/2019"
output: 
  html_document:
toc: true
toc_float: true
---

```{r setup}
library(tidyverse)
library(viridis)
library(p8105.datasets)
library(plotly)
```

#how much to set seed? should i make this out of my files i made during class since they connect to the website or create a whole new one?

```{r load and tidy data}
set.seed(1)

data("rest_inspec")

summary(rest_inspec)

rest_inspec = 
rest_inspec %>%
  janitor::clean_names() %>%
  filter(grade %in% c("A", "B", "C"), boro != "Missing") %>% 
  mutate(boro = str_to_title(boro)) %>%
  mutate(boro = as.factor(boro),
         critical_flag = as.ordered(critical_flag))

```

```{r boxplot}
rest_inspec %>%
  group_by(boro) %>%
  ggplot(aes(x = boro, y = score, color = boro)) + geom_boxplot()
  

```



set.seed(1)

data(nyc_airbnb)
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(rating = review_scores_location / 2) %>%
  select(
    neighbourhood_group, neighbourhood, rating, price, room_type, lat, long) %>%
  filter(
    !is.na(rating), 
    neighbourhood_group == "Manhattan",
    room_type == "Entire home/apt",
    price %in% 100:500)  %>% 
  sample_n(5000)

nyc_airbnb



Plotting with aesthetic options:

nyc_airbnb %>%
  mutate(text_label = str_c("Price: $", price, '\nRating: ', rating)) %>% 
  plot_ly(
    x = ~lat, y = ~long, type = "scatter", mode = "markers",
    color = ~price, text = ~text_label, alpha = 0.5)

```

Plotly plots:



#nyc_airbnb %>%
  mutate(text_label = str_c("Price: $", price, '\nRating: ', rating)) %>% 
  plot_ly(
    x = ~lat, y = ~long, type = "scatter", mode = "markers",
    color = ~price, text = ~text_label, alpha = 0.5)

#nyc_airbnb %>% 
  count(neighbourhood) %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, n)) %>% 
  plot_ly(x = ~neighbourhood, y = ~n, color = ~neighbourhood, type = "bar")

#nyc_airbnb %>% 
mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  plot_ly(y = ~price, color = ~neighbourhood, type = "box",
          colors = "Set2")

